Manuscript Template for a Data Analysis Project

### 2023-02-09 products/manuscript/MANU.qmd
removed (../../) and code chunks causing issues with rendering

```{r warning = false}
setwd("../../")
pov <- read_xlsx(here("data/raw_data/economics_22.xlsx"), sheet = "poverty")

@@

```{r}
#| label: tbl-summarytable
#| tbl-cap: "Data summary table."
#| echo: FALSE
resulttable=readRDS("../../results/summarytable.rds")
knitr::kable(resulttable)
```

@@

```{r}
#| label: fig-result
#| fig-cap: "Height and weight stratified by sex."
#| echo: FALSE
knitr::include_graphics(here("results","height_weight_stratified.png"))
```

@@

```{r}
#| label: tbl-resulttable2
#| tbl-cap: "Linear model fit table."
#| echo: FALSE
resulttable2 = readRDS(here("results","resulttable2.rds"))
knitr::kable(resulttable2)
```

>>>>

```{r warning = FALSE}
pov <- read_xlsx(here("data/raw_data/economics_22.xlsx"), sheet = "poverty")

@@

@@

@@
